---
title: "ANOVA APPLICATION"
output: html_document
---

## Objective:
The main objective of this work is to applied ANOVA test to explore the effect of three types of diet on losing weight.
The data we have is from **kaggle** website  https://www.kaggle.com/zaranadoshi/anova-diet

```{r}
library(tidyverse)

```
First, we should import data

```{r}
DataDiet=read.csv("~/Documents/master/s3/ANOVA/Diet.csv")
head(DataDiet)
```

We now create a new variable **weightlost = weight - weight6week** that indicating weight lost after 6 weeks of taking diet (a, b or c) in both men and women


```{r}
DataDiet=DataDiet %>% mutate(weightLost=weight-weight6weeks) %>% select(-3,-4)
head(DataDiet)
```

Let's create a linear model that predicts weight loss based on diet and gender
```{r}
model=lm(weightLost~Diet*gender,data=DataDiet)
residus=residuals(model)
```
## Checking the conditions for applying  ANOVA

### shapiro test to check normality.
The null hypothesis of this test is that the population comes from a normal distribution

```{r}
shapiro.test(residus)
```
Since the p-value is greater than alpha > 5%, so we accept the null hypothesis.\\

We can also check the normality graphically using the histogram

```{r}
hist(residus,prob='T')
curve(dnorm(x,mean(residus),sd(residus)),add=T,col="red")

```

### homocedacité test
The null hypothesis of this test is that the variance is the same in all samples.
```{r}
bartlett.test(residus~Diet,data=DataDiet)
bartlett.test(residus~gender,data=DataDiet)

```
We also accept the null hypothesis for both cases because the p-values are above the 5% range.

**Since the conditions are satisfied, we can apply the anova method on our data**

### anova table
```{r}
anova(model)
```
The results of the **ANOVA** table means that the Diet variable is the only one that has an effect on weight loss, and there is no interaction between diet and gender variables


### Tukey test

We will now see which type of Diet is better for weight loss
```{r}
mod=aov(weightLost~Diet*gender,data=DataDiet)
TukeyHSD(mod,"Diet")
```
According to the results of calculations there is a significant deference between **C modality** and others


```{r}
plot(DataDiet$Diet,DataDiet$weightLost)
```

**Conclusion**
The most suitable diet for losing weight is the C diet.
